Dark Control:\\ A Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-11-28 paper/paper.tex
modestify title
fixed some bugoos

% CRITICISM
% \paragraph{Main criticisms.}
Despite its popularity, criticism against the FEP has arisen over the years,
some of which is outlined in the following.
The main algorithm for minimizing free energy $F_G^R(\x)$ is the \textit{wake-sleep algorithm}
\citep{dayan1995helmholtz}. As P. Dayan and G. Hinton  noted,
a crucial drawback of the wake-sleep algorithm (and therefore of theories like the FEP \citep{friston2010free} based on it) is that it involves a pair
of forward (generation) and backward (recognition) models $p_G$ and $p_R$ respectively that
together do not correspond to optimization of (a bound of) the marginal likelihood,
because KL divergence is not symmetric in its arguments.
The brain is therefore unlikely to implement the wake-sleep algorithm or a variant thereof.
\begin{wrapfigure}{r}{.37\linewidth}
  \centering
  \includegraphics[width=1.\linewidth]{darkroom_resized.png}
  \caption{\textbf{The dark room experiment.} An intelligent agent situated
  in a light-deprived closed space can be used
  as a thought experiment for the complete absence
  of external sensory input.
  % The free-energy principle theory paradoxally predicts that such an agent would remain quietly in this room, such it perfectly predict all sensory input from such an environment.
  % However such behavior is not observed in humans or any animals: the agent would strive to leave such an environment in search of more ``interesting'' worlds.
  }
  \label{fig:darkroom}
\end{wrapfigure}

>>>>

% CRITICISM
% \paragraph{Main criticisms.}
Despite its popularity, criticism against the FEP has arisen over the years,
some of which is outlined in the following.
The main algorithm for minimizing free energy $F_G^R(\x)$ is the \textit{wake-sleep algorithm}
\citep{dayan1995helmholtz}. As P. Dayan and G. Hinton themselves noted,
a crucial drawback of the wake-sleep algorithm (and therefore of theories like the FEP \citep{friston2010free} based on it) is that it involves a pair
of forward (generation) and backward (recognition) models $p_G$ and $p_R$ respectively that
together do not correspond to optimization of (a bound of) the marginal likelihood,
because KL divergence is not symmetric in its arguments.
The brain is therefore unlikely to implement the wake-sleep algorithm or a variant thereof.
\begin{wrapfigure}{r}{.37\linewidth}
  \centering
  \includegraphics[width=1.\linewidth]{darkroom_resized.png}
  \caption{\textbf{The dark room experiment.} An intelligent agent situated
  in a light-deprived closed space is used
  as a thought experiment for the complete absence
  of external sensory input.
  % The free-energy principle theory paradoxally predicts that such an agent would remain quietly in this room, such it perfectly predict all sensory input from such an environment.
  % However such behavior is not observed in humans or any animals: the agent would strive to leave such an environment in search of more ``interesting'' worlds.
  }
  \label{fig:darkroom}
\end{wrapfigure}
